% Recommended placement:
% Insert this snippet in Section "Experimental Setup",
% after the paragraph that introduces models / datasets / truncation settings,
% and before the paragraph that starts with
% "We answer three questions."

\paragraph{Budget instantiation protocol.}
For all differential-sparsity and joint sparse-quant settings, we do not fix a single universal three-level policy in advance.
Instead, under each target average sparsity budget, we instantiate the policy using the calibration procedure described in
Section~\ref{sec:budget-config}. Concretely, for a target budget $B \in \{0.5, 0.7\}$, we construct a feasible candidate set
of three-level configurations $c = ([p_0,p_1,p_2], \rho_1)$ satisfying the budget constraint in
Equation~\eqref{eq:budget_constraint}, evaluate these candidates on a small held-out calibration split, and select the
best-performing configuration under the same budget. We then re-evaluate the selected configuration on a disjoint validation
split before running the full LongBench evaluation.

Unless otherwise noted, the calibration protocol keeps the remaining selection hyperparameters fixed and only searches the
budget allocation itself, namely the dense/partial/evict proportions and the intermediate sparsity level. This protocol
ensures that matched-budget comparisons are fair in two senses: the compared methods have the same target average sparsity,
and the differential policy is instantiated through the same calibration procedure rather than through hidden task-specific
manual tuning. For task-adaptive results, calibration and validation are performed separately for each task; for shared-policy
results, one calibrated configuration is selected and then reused across the evaluation tasks.

In the experiments reported below, we use a small calibration subset and a disjoint validation subset drawn from the same
benchmark pool with fixed random seeds. This lightweight protocol is sufficient to expose task-level differences in preferred
budget allocation while keeping the tuning cost negligible compared with full evaluation.

% Optional concrete version if you want to state exact numbers.
% Replace the paragraph above with the following sentence if you want explicit protocol details:
%
% In our default protocol, we use 10 calibration examples and 30 validation examples
% per task, sampled with fixed random seeds, and keep the two subsets disjoint.
